---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# boxplotstats

<!-- badges: start -->
[![R-CMD-check](https://github.com/selkamand/boxplotstats/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/boxplotstats/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/selkamand/boxplotstats/branch/main/graph/badge.svg)](https://app.codecov.io/gh/selkamand/boxplotstats?branch=main)
![GitHub Issues or Pull
Requests](https://img.shields.io/github/issues-closed/selkamand/boxplotstats)
[![CodeSize](https://img.shields.io/github/languages/code-size/selkamand/boxplotstats.svg)](https://github.com/selkamand/boxplotstats)
![GitHub last
commit](https://img.shields.io/github/last-commit/selkamand/boxplotstats)
<!-- badges: end -->

The `boxplotstats` package provides functions to calculate and visualize boxplot summary statistics for numeric data, including handling grouped data.

The most common use-case for this package is  you have lots of data e.g. from. bootstrapping experiments that you don't want to store, but you may want to plot.


## Installation

You can install the development version of boxplotstats from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/boxplotstats")
```

## Usage

### Calculate Boxplot Summary Statistics
To calculate boxplot summary statistics for a single numeric vector:

```{r example}
library(boxplotstats)

# Example numeric vector
vec <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 100)

# Calculate boxplot statistics
boxplot_stats <- calculate_boxplot_stats(vec)

# Print the results
print(boxplot_stats)
```

For a more complex example with outliers:


```{r }
# Numeric vector with outliers
vec_with_outliers <- c(rep(1, times = 3), 1:10, 22, 23)

# Calculate boxplot statistics
boxplot_stats_with_outliers <- calculate_boxplot_stats(vec_with_outliers)

# Print the results
print(boxplot_stats_with_outliers)
```

### Calculate Boxplot Summary Statistics for Multiple Groups

To calculate boxplot summary statistics for multiple groups:

```{r}
# Example values and group IDs
values <- c(1, 1, 1, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 22, 23, 8, 8, 8, 12, 13, 14, 15, 30, 31)
ids <- c("b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b1", "b2", "b2", "b2", "b2", "b2", "b2", "b2", "b2", "b2")

# Calculate boxplot statistics for multiple groups
group_stats <- calculate_boxplot_stats_for_multiple_groups(values, ids)

# Print the results
print(group_stats)
```



### Visualise Boxplots

```{r, fig.height=3, fig.width=6}
# Plot a single boxplot
plot_boxplot_stats(boxplot_stats_with_outliers)

# Plot multiple boxplots
plot_boxplot_stats(group_stats, ylab = "Identifiers")
```

